\documentclass{article}
\usepackage{bubblecv}

\begin{document}


\begin{cv}[avatar]{Mattia Giurato, PhD}{AOCS \& GNC Specialist at D-Orbit}


\cvsection[summary]{Profile}  %-----------------------------------------------------------

Aerospace engineer with a Ph.D. in multirotor GNC and 10+ years of experience spanning UAV control, embedded flight software, and spacecraft AOCS. Currently working as AOCS Subsystem Leader at D-Orbit, with hands-on expertise across the full V\&V pipeline (MIL/SIL/PIL/HIL) and ECSS-compliant model-based design.

\cvsection[work]{Work experience}  %------------------------------------------------------

\begin{cvevent}[Present][Jun. 2024]
    \cvname{AOCS \& GNC Specialist}
    \cvdescription{D-Orbit s.p.a., Como, Italy}
\end{cvevent}

\begin{cvevent}[Jun. 2024][Feb. 2020]
    \cvname{Co-Founder and CTO}
    \cvdescription{ANT-X s.r.l., Milan, Italy}
\end{cvevent}

\begin{cvevent}[Oct. 2020][Feb. 2020]
    \cvname{Post-Doctoral Researcher}
    \cvdescription{Department of Aerospace Science and Technologies
Politecnico di Milano, Italy}
\end{cvevent}

\begin{cvevent}[Jul. 2019][Mar. 2019]
    \cvname{Visiting Researcher}
    \cvdescription{LAAS - CNRS Toulouse, France}
\end{cvevent}

\begin{cvevent}[Nov. 2016][Jan. 2016]
    \cvname{Research Assistant}
    \cvdescription{Department of Aerospace Science and Technologies
Politecnico di Milano, Italy}
\end{cvevent}

\cvsection[education]{Education}  %------------------------------------------------------

\begin{cvevent}[Jan. 2020][Nov. 2016]
    \cvname{Aerospace Engineering, Ph.D.}
    \cvdescription{Politecnico di Milano, Italy}
\end{cvevent}

\begin{cvevent}[Dec. 2015][Oct. 2013]
    \cvname{Automation and Control Engineering, M.Sc.}
    \cvdescription{Politecnico di Milano, Italy}
\end{cvevent}

\begin{cvevent}[Oct. 2013][Sep. 2010]
    \cvname{Automation and Control Engineering, B.Sc.}
    \cvdescription{Politecnico di Milano, Italy}
\end{cvevent}

\cvsection[target]{Certifications}  %----------------------------------------------------------

\begin{cvevent}[Feb. 2022]
    \cvname{Professional License in Industrial Engineering}
    \cvdescription{Esame di Stato, Ingegnere Industriale Sez. A — FOIM, Milano}
\end{cvevent}

\begin{cvevent}[Mar. 2014]
    \cvname{Simulink for System and Algorithm Modeling}
    \cvdescription{MathWorks Training Service}
\end{cvevent}

%\begin{cvevent}[Feb. 2017]
%    \cvname{Creative Technologies in the Classroom 101 Trainer}
%    \cvdescription{Arduino}
%\end{cvevent}


%\cvsection[projects]{Personal Projects}  %----------------------------------------------------------

%\begin{cvevent}[Oct. 2023][May 2021]
%    \cvname{Drift car data telemetry for the Italian Drift Championship}
%\end{cvevent}

%\begin{cvevent}[2019][2018]
%    \cvname{UAV LAB}
%    \cvdescription{Organized and lectured in the "Innovative Teaching Methods" course held at the Drone laboratory of the Department of Aerospace Science and Technologies, Politecnico di Milano, Italy}
%\end{cvevent}

%\begin{cvevent}[2018]
%    \cvname{AICA - Robotics Certification}
%    \cvdescription{Developed the syllabus for the Robotics Certification in collaboration with WebScience and AICA}
%\end{cvevent}

%\begin{cvevent}[2017]
%    \cvname{Digital Brick - Arduino CTC 101}
%    \cvdescription{Organized and lectured in a hands-on course on Arduino coding in collaboration with WebScience and Arduino}
%\end{cvevent}

%\begin{cvevent}[2014]
%    \cvname{Aerospace System, Guidance, Navigation, and Control}
%    \cvdescription{Organized and lectured in a theoretical and practical course provided through collaboration between Skyward Experimental Rocketry and The MathWorks}
%\end{cvevent}

%\begin{cvevent}[2015][2013]
%    \cvname{Skyward Experimental Rocketry}
%    \cvdescription{Served as the leader of the Rocket Control Team}
%\end{cvevent}

\cvsidebar %-----------------------------------------------------------------------------

\cvsection[contact]{Contact}  %----------------------------------------------------------

\begin{cvitem}[Envelope][4]
    \textbf{Email}\\
    \href{mailto:mattia.giurato@gmail.com}{\texttt{mattia.giurato@gmail.com}}
\end{cvitem}

\cvseparator[3]
\begin{cvitem}[Phone][4]
    \textbf{Phone}\\
    \href{tel:+393406402959}{\texttt{+39 340 640 2959}}
\end{cvitem}

\cvseparator[3]
\begin{cvitem}[Home][4]
    \textbf{Address}\\
    Milano, Italy
\end{cvitem}

\cvseparator[3]
\begin{cvitem}[Globe][4]
    \textbf{Website}\\
    \href{https://mgiurato.eu/}{\texttt{mgiurato.eu}}
\end{cvitem}

\cvsection[publications]{Soft skills}  %-----------------------------------------------------------

\cvseparator
\begin{cvitem}
    Communication
\end{cvitem}

\cvseparator
\begin{cvitem}
    Management
\end{cvitem}

\begin{cvitem}
    Creativity
\end{cvitem}

\begin{cvitem}
    Critical thinking
\end{cvitem}

\cvseparator
\begin{cvitem}
    Goal Oriented
\end{cvitem}

\begin{cvitem}
    Passionate
\end{cvitem}

\cvsection[skills]{Hard skills}  %-----------------------------------------------------------

\cvseparator
\begin{cvitem}
    MATLAB \& Simulink (code generation)
\end{cvitem}

\begin{cvitem}
    C/C++, Python
\end{cvitem}

\begin{cvitem}
    ROS / ROS2, Gazebo
\end{cvitem}

\begin{cvitem}
    PX4, Ardupilot
\end{cvitem}

\begin{cvitem}
    Embedded systems, RTOS
\end{cvitem}

\cvseparator
\begin{cvitem}
    ECSS, Savoir
\end{cvitem}

\begin{cvitem}
    MIL / SIL / PIL / HIL
\end{cvitem}

\begin{cvitem}
    Jira, Confluence, Jama, Codebeamer
\end{cvitem}

\begin{cvitem}
    Git, Docker, Linux
\end{cvitem}

\cvseparator
\begin{cvitem}
    UAV piloting (A1/A3, A2, IT-STS)
\end{cvitem}

\begin{cvitem}
    UAV design, integration and testing
\end{cvitem}

\begin{cvitem}
    3D modelling (SolidWorks, CATIA)
\end{cvitem}

%\begin{cvitem}
%    Mechanical design
%\end{cvitem}

%\begin{cvitem}
%    3D printing
%\end{cvitem}

%\begin{cvitem}
%    Physical dexterity
%\end{cvitem}

\cvsection[languages]{Languages}  %--------------------------------------------------------

\cvskill{Italian}{Mother-tongue}{1.0}
\cvskill{English}{Fluent}{0.9}


\end{cv}

\cvfootnote{
    \tiny I agree to the processing of personal data provided in this document for realising the recruitment process pursuant to the Personal Data Protection Act of 10 May 2018 (Journal of Laws 2018, item 1000) and in agreement with Regulation (EU) 2016/679 of the European Parliament and of the Council of 27 April 2016 on the protection of natural persons with regard to the processing of personal data and on the free movement of such data, and repealing Directive 95/46/EC (General Data Protection Regulation)
}

\end{document}
